### 2015-03-02 src/4_OnlineLearning.tex
efficient computation ready

>>>>

Despite the bias-variance tradeoff provides a conceptual framework for
determining a good model, is not directly useful. Some popular methods
for determine model selection are:

\begin{itemize}
    \item Akaike information criterion (AIC) (Akaike, 1974)
    \item Bootstrap-based selection (Efron and Tibshirani, 1997)
    \item Cross-validation (Stone, 1974)
\end{itemize}

On the other hand, $\lambda$ can also be used to reduce computational time as it
is shown in equation~(\ref{eq:taylor}). Golub (~\cite{golub1965}) suggested that
$\lambda$ be chosen so that:

\[
\frac{\lambda}{\lambda + \delta^2} < 0.1
\]

\noindent where $\delta$ is a lower bound of the smallest non-zero singular
value $\sigma_k$. One approach is to choose the greatest lower bound for
$\delta=\sigma_k$. Hence:

\[
\frac{\lambda}{\lambda + \sigma_k^2} < 0.1
\]

\noindent if we choose $\lambda=\beta \sigma_k^2$ then we get the following
relation:

\[
\frac{\beta \sigma_k^2}{\beta \sigma_k^2 + \sigma_k^2} =
\frac{\beta}{\beta+1} < 0.1 \Rightarrow \beta < \frac{1}{9}  
\]

Experiments done by ~\cite{coleman+sun2010} have shown that $\beta = 0.01$
produces satisfactory results. This means that $\lambda = 0.01 \sigma_k^2$.

However, get $\sigma_k$ imply obtaining first the SVD, which is
computational expensive.

Since the algorithm presented by ~\cite{coleman+sun2010} already compute the QR
factorization of the matrix $\mathbf{A}$ they show a procedure for getting
a $\lambda$ approximation using QR.

\begin{enumerate}
\item Compute QR factorization: $\mathbf{A} = \mathbf{Q_1R_1}$
\item Let $\mathbf{W}$ denote the set of absolute values of the nonzero diagonal
elements of $\mathbf{R_1}$. Let $w_{\text{min}}$ and $w_{\text{max}}$ denote the
smallest and largest elements of $\mathbf{W}$ respectively. Both 
$\lambda_1 = \hat{\beta} w_{\text{min}}^2$
$\lambda_2 = \hat{\beta} \frac{w_{\text{min}}^2}{w_{\text{max}}^2}$ where
$\hat{\beta}=0.00025$ produce satisfactory results.
\item The $\lambda_{\text{QR}}$ approximation is obtained as:
$\lambda_{\text{QR}} = \frac{\lambda_1 + \lambda_2}{2}$  
\end{enumerate}
